\section{Introduction}
The mechanisms behind lung adenocarcinoma, specifically those of individual A549 cells.
Computational techniques can help with a better understanding of the behaviour of these cancer cells.
% , together with a calcium channel extension introduced in \cite{2024-calcium-channels}, 
We work with the A549 model introduced in \cite{2021-A549-model,2024-calcium-channels}, reimplementing the model in the Rust programming language and performing a number of numerical optimizations such as adaptive timestepping.
Physical measurements are obtained using a \textit{Patch-Clamp System}, where one records the current through the membrane given a voltage protocol.
% We also verify the model's performance in \textit{Floating} mode, as compared to an individual simulation of the estimated number of channels.
In order to find appropriate parameters for the model, an optimization procedure is performed.
Multiple optimization approaches for the solution of the corresponding inverse problem (fitting model parameters to measurement data) are put in comparison.

\input{chapters/methods.tex}
\input{chapters/results.tex}

\section{Outlook}
Efforts to further enhance and complete the first electrophysiological cancer cell model simulation were fruitful, resulting in a new library implementation, an improved inverse problem solution technique and a live in-browser simulation dashboard.

Numerically, the stability of the simulation varies greatly with the time step state change tolerance $\Delta^{\rm tol}$, this could be improved using a higher-order integration scheme.

Regarding the simulation dashboard, there are still many adjustments that could improve and enable further usage perspectives.
Specifically, it would be effective to add visual handles for adjusting the number of channels per type and weigh their individual contributions, for instance.

Another useful extension would be to enable the interface-based integration of further ion channel types as part of the simulation, without the need to specifically modify the pre-compiled Rust source code.
