\documentclass[USenglish,twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage[big,online]{dgruyter}
% \usepackage[sort&compress,square,numbers]{natbib}
\usepackage[backend=biber, citestyle=numeric, bibstyle=authoryear, hyperref=true, sorting=none, maxbibnames=99]{biblatex}
\usepackage{csquotes}
\usepackage{times}

\addbibresource{../literature/sources.bib}

% TODO: https://en.wikipedia.org/wiki/Non-negative_least_squares

\begin{document}
  %%%--------------------------------------------%%%
  %%% Please do not alter the following lines: %%%
  %%%--------------------------------------------%%%
  %\articletype{Proceedings}
  %\aop
  \DOI{10.1515/}
  \openaccess
  \pagenumbering{gobble}
  %%%--------------------------------------------%%%

  \title{Performance optimization of the A549 electrophysiological cancer cell model and live simulation dashboard}
  \runningtitle{Computational model of ion channel current}
  %\subtitle{Insert subtitle if needed}

  \author*[1]{Peter Waldert}
  \author[1]{Sonja Langthaler}
  % \author[2]{Third Author (Name Surname)}
  % \author[3]{Fourth Author (Name Surname)}
  \runningauthor{P.~Waldert et al.}

  \affil[1]{\protect\raggedright
    Institute of Health Care Engineering with European Testing Center for Medical Devices, Graz University of Technology, Graz, Austria, e-mail: peter.waldert@tugraz.at}
  % \affil[2]{\protect\raggedright
  %   Institution (if same for both authors), city, country}
  % \affil[3]{\protect\raggedright
  %   Institution, city, country}

  \abstract{Please insert your abstract here. Remember that online
    systems rely heavily on the content of titles and abstracts to
    identify articles in electronic bibliographic databases and search
    engines. We ask you to take great care in preparing the abstract.}

  \keywords{Please insert your keywords here, separated by commas.}

  \maketitle

  \section{Headline 1st level}

  Please insert your manuscript here \cite{2021-A549-model}.

  \vspace{1cm}

  %\begin{acknowledgement}
  %\end{acknowledgement}

  \textsf{\textbf{Author Statement}}\\
  Research funding: The author state no funding involved. Conflict of interest: Authors state no conflict of interest. Informed consent: Informed consent has been obtained from all individuals included in this study. Ethical approval: The research related to human use complies with all the relevant national regulations, institutional policies and was performed in accordance with the tenets of the Helsinki Declaration, and has been approved by the authors' institutional review board or equivalent committee.

  \printbibliography
\end{document}
